What is happening on Twitter? A framework for student research projects with tweets

### 2020-11-03 Rmd/jse-special-issue-2020-november-anon.Rmd
updates prior to resubmission

---
title: "What is happening on Twitter? A framework for student research projects with tweets"
author: "Frederick J. Boehm and Bret M. Hanlon"
date: ""
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    keep_tex: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

>>>>

---
title: "What is happening on Twitter? A framework for student research projects with tweets"
date: ""
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    keep_tex: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---
